A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-05-09 paper.Rmd
remove curly quotes
use new preamble template

---
title: A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility
output:
  bookdown::pdf_book:
    base_format: rmarkdown::pdf_document
bibliography: references.bib
---

```{r setup}
knitr::opts_chunk$set(echo = FALSE,
                      out.width = "100%")
```

> “Data! data! data!" he cried impatiently. "I can't make bricks without clay.” - Sherlock Holmes (PBS Series, 2010-2017)

>>>>

---
title: A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility
output:
  bookdown::pdf_document2:
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
header-includes: 
  - \linespread{2} 
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.width = "100%")
```

> "Data! data! data!" he cried impatiently. "I can't make bricks without clay." - Sherlock Holmes (PBS Series, 2010-2017)
